---
title: "shinySBM report"
format: html
params:
  upload: NULL
  sbm: NULL
  options: NULL
---

```{r setup, echo=FALSE}
R <- purrr::map(params,~if(identical(.x,"NA")){NA}else{.x})
show_mat <- !identical(R$upload,NA)
show_sbm <- !identical(R$sbm,NA)
is_bipartite <- R$upload$Dataset$type == 'bipartite'
```


```{r child1, child=if(show_mat) 'child_imported_en.Rmd'}
```

un visuel de Matrice attention indiquer si col and row have been inversed

```{r child2, child=if(show_mat) 'child_imported_visual.Rmd'}
```

## Résultats du Modèle à Blocks stochastique

```{r child3, child=if(show_sbm) 'child_sbm_en.Rmd'}
```

## Visualisation du SBM

```{r child4, child=if(show_sbm) 'child_sbm_visual.Rmd'}
```


# Références

1.  Chiquet J, Donnet S, Barbillon P (2023).  sbm: Stochastic Blockmodels. R package version 0.4.5,  
  [https://CRAN.R-project.org/package=sbm](https://CRAN.R-project.org/package=sbm).
  
2.  Vanrenterghem T, Julie A (2023).  ShinySBM: A shiny application for Stochastic Blockmodels. R package on gitlab,  
  [https://forgemia.inra.fr/theodore.vanrenterghem/shinySbm](https://forgemia.inra.fr/theodore.vanrenterghem/shinySbm).
  
3.  We are grateful to the INRAE MIGALE bioinformatics facility (MIGALE, INRAE, 2020. Migale bioinformatics Facility, doi:
  10.15454/1.5572390655343293E12) for providing help and/or computing and/or storage resources.
  
